Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-26 paper/ijcai/paper.tex

Table \ref{table:st} presents the statistics to determine if the
observed results are statistically significant. Shapiro-Wilk tests the
null hypothesis that results are drawn from a normal distribution. The
test is perfomed for all techniques and its variants. With $99\%$ of
confidence, the results tell us that the distributions are not
normal. Given that $C$ is not normally distributed, we use Friedman, a
non-parametric statistical test of hypothesis. The null hypothesis is
that the ranking results of all techniques and variants are the
same. With $99\%$ confidence, the results show that the distributions
are distinct. To understand which techniques perform differently,
\ie{}, to answer the question \textit{Does \combpar{k} perform
  differently than \sfl{}$^{k}$}, we performed a Siegel post-hoc
analysis. Figure \ref{fig:performance} reports results. Each square
shows the statistical significance of the difference in diagnostic
accuracy amongst the different techniques--the lighter color and
smaller value of $p$ indicates higher significance. Based on these
results, it is possible to determine with $95\%$ confidence that the
performance of each pair of techniques is different.

>>>>

Table \ref{table:st} presents the statistics to determine if the
observed results are statistically significant. Shapiro-Wilk tests the
null hypothesis that results are drawn from a normal distribution. The
test is perfomed for all techniques and values of $k$. With $99\%$
confidence, the results tell us that the distributions are not
normal. Given that $C$ is not normally distributed, we used Friedman, a
non-parametric statistical test of hypothesis. The null hypothesis is
that the rankings obtained with all techniques and variants are the
same. With $99\%$ confidence, the results show that the distributions
are distinct. To understand which techniques perform differently,
\ie{}, to answer the question \textit{Does \combpar{k} perform
  differently than \sfl{}$^{k}$}, we performed a Siegel post-hoc
analysis. Figure \ref{fig:performance} reports results. Each square
shows the statistical significance of the difference in diagnostic
accuracy amongst the different techniques--the lighter color and
smaller value of $p$ indicates higher significance. Based on these
results, it is possible to determine with $95\%$ confidence that the
performance of each pair of techniques is different.
